### 2024-04-17 analysis/paper/paper.Rmd
minor changes, found issue with doubled roads, investigating

tsaBoundary <- read_sf(here(data_path_raw, "tsa27_boundaries.gpkg"))
#cost surface raster layer
tsaCost <- terra::rast(here(data_path_drvd, "old cost/input_cost.tif"))
dem <- terra::rast(here(data_path_drvd, "dem/input_cost.tif"))

>>>>

tsaBoundary <- read_sf(here(data_path_raw, "tsa27_boundaries.gpkg"))
#cost surface raster layer
tsaCost <- terra::rast(here(data_path_drvd, "input_cost.tif"))
dem <- terra::rast(here(data_path_drvd, "dem/input_cost.tif"))

### 2024-04-17 analysis/scripts/5_make_fig4.Rmd
minor changes, found issue with doubled roads, investigating

data_path_raw <- "analysis/data/raw_data/"
data_path_drvd <- "analysis/data/derived_data/TSA27"

@@

e_rds <- st_read(here::here(file.path(data_path_drvd, "input_roads.gpkg")))
p_rds <- st_read(here::here(file.path(data_path_drvd, "regular_1e-05_mst.gpkg")))
o_rds <- st_read(here::here(file.path(data_path_drvd, "../combined_revelstoke_roads.gpkg")))

@@

```

>>>>

data_path_raw <- "analysis/data/raw_data/"
data_path_drvd <- "analysis/data/derived_data/TSA27_real_cuts/dem"

@@

e_rds <- st_read(here::here(file.path(data_path_drvd, "../input_roads.gpkg")))
p_rds <- readRDS(here::here("analysis/data/derived_data/bench_results/result_mst_regular_1e-05_10_revelstoke_real.rds"))
o_rds <- st_read(here::here(file.path(data_path_drvd, "../../combined_revelstoke_roads.gpkg")))

@@

# p_rds_ilcp <- readRDS(here::here("analysis/data/derived_data/bench_results/result_ilcp_regular_1e-05_10_revelstoke_real.rds"))
# 
# write_sf(p_rds_ilcp, here::here("analysis/data/derived_data/bench_results/ilcp_regular_1e-05_10_revelstoke_real.gpkg"))
#  p_rds_mst <- readRDS(here::here("analysis/data/derived_data/bench_results/result_mst_regular_1e-05_10_revelstoke_real.rds"))
# 
# write_sf(p_rds_mst, here::here("analysis/data/derived_data/bench_results/mst_regular_1e-05_10_revelstoke_real.gpkg"))
```
